### 2024-05-20 intro.qmd
20240519 - football field diagram
20240520 - about the book

@@

@@

![Video of Prof. Benjamin Motz discussing statistics and fantasy football course.](images/motzVideo.mp4){width=100%}

>>>>

## About this Book {#sec-aboutBook}

@@

This book was originally written for a undergraduate-level course entitled, "Fantasy Football: Predictive Analytics and Empiricism".
The chapters provide an overview of topics that each could have its own class and textbook, such as [causal inference](causal-inference.qmd), [factor analysis](factor-analysis.qmd), [cluster analysis](cluster-analysis.qmd), [principal component analysis](pca.qmd), [machine learning](machine-learning.qmd), [cognitive biases](cognitive-bias.qmd), [modern portfolio theory](modern-portfolio-theory.qmd), [data visualization](data-visualization.qmd), [simulation](simulation.qmd), etc.
The book gives readers an overview of the breadth of the approaches to prediction and empiricism.
As a consequence, the book does not cover any one technique or approach in great depth.

@@

![Video of Prof. Benjamin Motz Discussing Statistics and His Fantasy Football Course.](images/motzVideo.mp4){width=100%}
